The Prevalence of E-Mail Header Injections on the World Wide Web

### 2016-05-19 Background/php.tex
rewrote code samples to anonymize the paper, removed references to myself and to asu

\lstset{language=PHP,caption={PHP program with e-mail header injection vulnerability.},label={code:phpemi}}
\begin{lstlisting}
$from = $_REQUEST['email'];
$subject = "Hello Sai Pc";
$message = "We need you to reset your password";
$to = "schand31@asu.edu";

// example attack string to be injected as the value for
// $_REQUEST['email'] => 'sai@sai.com\nCC:spc@spc.com'
$retValue = mail($to, $subject, $message, "From: $from");
// E-Mail gets sent to both schand31@asu.edu AND spc@spc.com
\end{lstlisting}

>>>>

\lstset{language=PHP,caption={PHP program with e-mail header injection vulnerability.},label={code:phpemi}}
\begin{lstlisting}
$from = $_REQUEST['email'];
$subject = 'Hello XYZ';
$message = 'We need you to reset your password';
$to = 'xyz@xyz.edu';

// example attack string to be 
// injected as the value for
// $_REQUEST['email'] => 
// 's@s.com\nCC:spc@spc.com'
$retValue = mail($to, $subject, $message, "From: $from");
// E-Mail gets sent to both 
// xyz@xyz.edu AND spc@spc.com
\end{lstlisting}

### 2016-05-19 Background/py.tex
fixing code samples
rewrote code samples to anonymize the paper, removed references to myself and to asu

\lstset{language=Python,caption={Python program with e-mail header injection vulnerability.},label={code:pyemi}}
\begin{lstlisting}
from email.parser import Parser
import cgi
form = cgi.FieldStorage()
to = form["email"] # input() exhibits the same behavior
msg = """To: """ + to + """\n
From: <user@example.com>\n
Subject: Test message\n\n
Body would go here\n"""

f = FeedParser() # Parser.parsestr() also 
# contains the same vulnerability
f.feed(msg)
headers = FeedParser.close(f)

# attack string => 'sai@sai.com\nBCC:spc@spc.com'
# for form["email"]

# both to:sai@sai.com AND bcc:spc@spc.com 
# are added to the headers
print 'To: %s' % headers['to']
print 'BCC: %s' % headers['bcc']
\end{lstlisting}

>>>>

\lstset{language=Python,caption={Python program with e-mail header injection vulnerability.},label={code:pyemi}}
\begin{lstlisting}
from email.parser import Parser
import cgi
form = cgi.FieldStorage()
to = form["email"] # input() exhibits 
# the same behavior
msg = """To: """ + to + """\n
From: <user@example.com>\n
Subject: Test message\n\n
Body would go here\n"""

f = FeedParser() # Parser.parsestr() 
# also contains the same vulnerability
f.feed(msg)
headers = FeedParser.close(f)

# attack string => 
# 's@s.com\nBCC:spc@spc.com'
# for form["email"]

# to:s@s.com AND bcc:spc@spc.com 
# are added to the headers
print 'To: %s' % headers['to']
print 'BCC: %s' % headers['bcc']
\end{lstlisting}

### 2016-05-19 Discussion/limits.tex
rewrote code samples to anonymize the paper, removed references to myself and to asu

       	\lstset{language=HTML,caption={E-Mail field checker - false positives, the system\\incorrectly classifies this as an e-mail form.},label={code:false_positive}}
       	\begin{lstlisting}
       	<form method="post">
       	E-Mail us if you have any questions!!
       	<input type="text" name="query"><br>
       	<input type="submit" value="Search">
       	</form>
       	\end{lstlisting}

@@

\lstset{language=HTML,caption={HTML page with e-mail form, written in a different language - French.},label={code:htmlfrench}, literate=%
	{é}{{\'e}}1}
\begin{lstlisting}
<!doctype html>
<html lang="fr">
<head>
<meta charset="utf-8">
<meta name="author" content="Sai Pc">
<title>Mock Email</title></head>
<body>
<form action="{Replace with path to back-end}" method="post">
<input type="text" placeholder="courrier électronique"
	name="courrier_électronique"><br>
<textarea name="msg" rows="20" cols="120"></textarea>
<input type="submit" value="courrier électronique!">
</form></body>
</html>
\end{lstlisting}

>>>>

       	\lstset{language=HTML,caption={E-Mail field checker - false positives, the system incorrectly classifies this as an e-mail form.},label={code:false_positive}}
       	\begin{lstlisting}
<form method="post">
E-Mail us if you have any questions!!
<input type="text" name="query"><br>
<input type="submit" value="Search">
</form>
       	\end{lstlisting}

@@

\lstset{language=HTML,caption={HTML page with e-mail form, written in a different language - French.},label={code:htmlfrench}, literate=%
	{é}{{\'e}}1}
\begin{lstlisting}
<!doctype html>
<html lang="fr">
<head>
<meta charset="utf-8">
<meta name="author" content="XYZ">
<title>Mock Email</title></head>
<body>
<form action="{path-to-back-end}" method="post">
<input type="text" placeholder="courrier électronique"
	name="courrier_électronique"><br>
<textarea name="msg" rows="20" cols="120"></textarea>
<input type="submit" value="courrier électronique!">
</form></body>
</html>
\end{lstlisting}

### 2016-05-19 System/proof_of_concept.tex
chap4 prelim edit
rewrote code samples to anonymize the paper, removed references to myself and to asu

\lstset{language=HTML,caption={HTML page for showcasing e-mail header injection, a simple front-end for our examples.},label={code:html}}
\begin{lstlisting}
<!doctype html>
<html lang="en">
<head>
<meta charset="utf-8">
<meta name="author" content="Sai Pc">
<title>Mock Email</title>
</head>
<body>
<form action="{Replace with path to back-end}" method="post">
<input type="text" placeholder="Email" name="email" id="e-mail"><br>
<textarea name="msg" rows="20" cols="120"></textarea>
<input type="submit" value="Email Me!">
</form>
</body>
</html>
\end{lstlisting}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=14cm, height=8cm]{System/EMI_Postman_Ruby}
	\caption[\titlecap{Fuzzing a request for the Ruby backend}]{Fuzzing a request for the Ruby backend, the payload can be seen inside the address bar.}
	\label{fig:postmanruby}
\end{figure}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=14cm, height=8cm]{System/EMI_Mailcatcher_Ruby}
	\caption[\titlecap{E-Mail header injection proof of concept - Ruby}]{E-Mail header injection proof of concept - Ruby, we can see that multiple headers (bcc, x-check, subject) have been inserted into the resulting e-mail.}
	\label{fig:mailcatcherruby}
\end{figure}

>>>>

\lstset{language=HTML,caption={HTML page for showcasing e-mail header injection, a simple front-end for our examples.},label={code:html}}
\begin{lstlisting}
<!doctype html>
<html lang="en">
<head>
<meta charset="utf-8">
<meta name="author" content="XYZ">
<title>Mock Email</title>
</head>
<body>
<form action="{path-to-back-end}" method="post">
<input type="text" placeholder="Email" name="email" id="e-mail"><br>
<textarea name="msg" rows="20" cols="120"></textarea>
<input type="submit" value="Email Me!">
</form>
</body>
</html>
\end{lstlisting}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=\linewidth]{System/EMI_Postman_Ruby}
	\caption[\titlecap{Fuzzing a request for the Ruby backend}]{Fuzzing a request for the Ruby backend, the payload can be seen inside the address bar.}
	\label{fig:postmanruby}
\end{figure}

\begin{figure}[!htbp]
	\centering
	\includegraphics[width=\linewidth]{System/EMI_Mailcatcher_Ruby}
	\caption[\titlecap{E-Mail header injection proof of concept - Ruby}]{E-Mail header injection proof of concept - Ruby, we can see that multiple headers (bcc, x-check, subject) have been inserted into the resulting e-mail.}
	\label{fig:mailcatcherruby}
\end{figure}

### 2016-05-19 paper.tex
rewrote code samples to anonymize the paper, removed references to myself and to asu

\documentclass{sig-alternate-05-2015}

\usepackage[square,numbers]{natbib}
\usepackage[justification=centering]{caption}
\usepackage[pageanchor=true,plainpages=false,pdfpagelabels,bookmarks,bookmarksnumbered,hidelinks]{hyperref}
\usepackage{color}
\definecolor{mygray}{rgb}{0.6,0.6,0.6}
\definecolor{lightgray}{rgb}{0.92,0.92,0.92}
\definecolor{darkgreen}{rgb}{0,0.7,0}

@@

% default options for listings
\usepackage{listings}
\usepackage{listingsutf8}
\usepackage{textcomp}     % access \textquotesingle
\lstset{
	backgroundcolor=\color{lightgray},
	basicstyle=\small,
	breaklines=true, 
	captionpos=b,
	commentstyle=\color{darkgreen}, 
	frame=single,
	keywordstyle=\color{blue}, 
	numbers=left,
	numbersep=5pt,
	numberstyle=\tiny\color{mygray},
	rulecolor=\color{black},
	showstringspaces=false,
	upquote=true
}

>>>>

\documentclass{sig-alternate-05-2015}
\usepackage[T1]{fontenc}
\usepackage[square,numbers]{natbib}
\usepackage[justification=centering]{caption}
\usepackage[pageanchor=true,plainpages=false,pdfpagelabels,bookmarks,bookmarksnumbered,hidelinks]{hyperref}
\usepackage{color}
\definecolor{mygray}{rgb}{0.6,0.6,0.6}
\definecolor{lightgray}{rgb}{0.92,0.92,0.92}
\definecolor{darkgreen}{rgb}{0,0.7,0}

@@

% default options for listings
\usepackage{listings}
\usepackage{listingsutf8}
\usepackage{textcomp}     % access \textquotesingle
\lstset{
	backgroundcolor=\color{lightgray},
	basicstyle=\ttfamily,
	breaklines=true, 
	captionpos=b,
	commentstyle=\color{darkgreen}, 
	frame=single,
	keywordstyle=\color{blue}, 
	numbers=left,
	numbersep=5pt,
	numberstyle=\tiny\color{mygray},
	rulecolor=\color{black},
	showstringspaces=false,
	upquote=true
}
